Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-19 paper/paper.tex
up to IV.B

\Mar{--------------------- I am here...}

@@

The goal of the Reverse Engineering step is to extract options from
the malicious traffic produced by the input example attacks. A rule
that contains these options captures the malicious traffic by
construction. \tname\ uses two strategies to extract options: 1)~the
field strategy applies to any protocol and 2)~the payload strategy
applies only to http.  The decision of which strategy to use is based
on the protocol associated with input traffic--the technique uses the
payload strategy if http is detected; otherwise, it uses the field
strategy. We elaborate these strategies in the following.

For the field strategy, \tname{} parses the input messages looking for
options associated with the data in the fields of
messages. Section~\ref{sec:rules-and-packets} shows the correspondence
between packet fields and some of the rule options from \suri\ and
Section~\ref{sec:active-recon} shows a concrete example illustrating a
case of this strategy. We obtained the option-field mapping
manually, from the \suri\ documentation.

Unfortunately, the relevant data for the option may be at the message
payload; not the fields. By analyzing our data set of rules, we found
that this occurs frequently in http attacks, which are prevalent. For
example, \percHttp\ of the \numrulessuri{} rules from the ruleset we
analyzed~\cite{emerging-threats-open} prescribe defenses against http
attacks. In addition, \percRulesWithContent{} of these rules contain
at least one content option. Figure~\ref{fig:rule-jboss} shows an
example of a rule that captures traffic containing the string
\CodeIn{"/HtmlAdaptor"} in the payload.
Figure~\ref{fig:distribution-contents} shows the distribution of
number of content options per rule for the data set mentioned
above. We limited the number of content options per rule to 10 in the
histogram for space. \MyComment{Rules without \CodeIn{content} options
  are an exception and half of the rules contain at least two
  \CodeIn{content} options.}  To sum up, handling content options for
http is very important.

The content strategy focuses on extracting content options from the
message payload. By inspecting existing rules, we found that these
options refer to sequences of characters separated by typical natural
language delimiters such as $\backslash$t, $\backslash$n,
$\backslash$r, and spaces. To find the values associated with these
options, \tname{} splits the payload in tokens using these delimiters.

@@

>>>>

@@

The goal of the Reverse Engineering step is to infer a \emph{seed
  rule} that captures the attack. To that end, \tname{} monitors the
traffic produced by the input example attack(s) and extracts options
from related messages. A rule that contains these options captures the
malicious traffic by construction. \tname\ uses two strategies to
extract options: 1)~field and 2)~payload. The field strategy applies
to any protocol whereas the payload strategy applies only to http.
The decision of which strategy to use is based on the protocol
associated with input traffic--\tname{} uses the payload strategy if
http is detected; otherwise, it uses the field strategy. We elaborate
these strategies in the following.

For the field strategy, \tname{} parses the input messages looking for
options associated with the data in the fields of
messages. Section~\ref{sec:rules-and-packets} shows the correspondence
between packet fields and some of the rule options from \suri\ and
Section~\ref{sec:active-recon} shows a concrete example where \tname{}
uses this strategy. ALthough we built the option-field mapping
manually, from the \suri\ documentation, this is a one-time activity.
Unfortunately, for http attacks, the relevant data for the options is
likely at the message payload; not the fields. By analyzing our data
set of rules, we found that this occurs frequently in http attacks,
which are prevalent. For example, \percHttp\ of the \numrulessuri{}
rules from the ruleset we analyzed~\cite{emerging-threats-open}
prescribe defenses against http attacks. In addition,
\percRulesWithContent{} of these rules contain at least one content
option. Figure~\ref{fig:rule-jboss} shows an example of a rule that
captures traffic containing the string \CodeIn{"/HtmlAdaptor"} in the
payload.  Figure~\ref{fig:distribution-contents} shows the
distribution of number of content options per rule for the data set
mentioned above. We limited the number of content options per rule to
10 in the histogram for space. \MyComment{Rules without
  \CodeIn{content} options are an exception and half of the rules
  contain at least two \CodeIn{content} options.}  To sum up, handling
content options for http is very important.

The content strategy focuses on extracting content options from the
message payload. By inspecting existing rules, we found that these
options refer to sequences of characters separated by natural language
delimiters such as $\backslash$t, $\backslash$n, $\backslash$r, and
spaces. To find the values associated with these options, \tname{}
splits the payload in tokens using these delimiters.

@@

\Mar{--------------------------------------------- I am here}
